Comparison of Terrain Following and Cut Cell Grids using a Non-Hydrostatic Model

### 2015-09-18 src/tf-cutcell-comparison/tf-cutcell-comparison.tex
make the motivation of terrain following advection test clearer

\subsection{Terrain following advection}
\TODO{make it clearer that we're trying to determine if non-orthogonality or misalignment of the flow is the primary source of error}

In the horizontal advection test, results were more accurate where the flow was aligned with the grid layers, and distortions in the BTF grid led to increased errors.  To determine the primary source of numerical error, we formulate a new tracer advection test in which the velocity field is everywhere tangential to the basic terrain following coordinate surfaces.  Misalignment on the SLEVE and cut cell grids is designed to challenge the advection scheme.

>>>>

\subsection{Terrain following advection}
In the horizontal advection test, results were least accurate on the BTF grid, where the grid was most non-orthogonal and flow was misaligned with the grid layers.  Here, we formulate a new tracer advection test in which the velocity field is everywhere tangential to the basic terrain following coordinate surfaces.  This test determines whether the primary source of numerical error is due to non-orthogonality or misalignment of the flow with grid layers.
